### 2022-10-07 Proposal/Proposal.tex
commit

\documentclass[12pt]{article}

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{Proposal: Influences of GDP in the U.S }
\author{Ginamarie Mastrorilli\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle

\paragraph{Introduction}
%Introduction: Introducing the topic and why you have chosen this topic (3–5 lines). 
%Mention briefly the current related research and cite relevant works.
Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
It is a "comprehensive measure of U.S economic activity." (add bea citation) 
GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
(cite K. Hema Divya) found that exchange rates and market indexes are important factors that influence an economies GDP. They also found that inflation is highly correlated, but not a significant influencer.

\paragraph{Specific Aims}
%Specific aims: Formulate a research question or hypothesis in the chosen topic.
% Describe briefly why you select such a question or hypothesis and its importance in the field (cite sources).
With so many economic factors and data readily avaiable, which variables should economists focus on?
When investigating U.S. Gross Domestic Product, the goal is to determine the relationship between variables and if those variables can help predict GDP.
If a variable tends to predict the value of GDP, then economists should focus more on these independent variables when forecasting Gross Domestic Product.
I decided to choose this topic because as an Economics minor, I have seen similar analysis, but have never had the opportunity to do this statistical analysis myself. 
This is important becuause even though there is an abdunace of resouces avaiable about GDP, this information can change based on country, variables used, and which years your data contains. 
Having the ability to accurately predict GDP is important because governments, corporations, and investors heavily take GDP into consideration when making decisions. (cite CFI article)

\paragraph{Data}
My data has been collected from the Federal Reserve Economic Data (FRED) website.
All of the datasets have been collected seperately and compiled into one dataset. 
There are seven variables and sixty seven observations in this dataset. 
My dependent variable is Gross Domestic Product (GDP). 
My independent variables are Population (POP), Nominal Broad U.S Dollar Index (NBUSDI), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Business Sector Labor Productivity (BSLP). 
The dataset contains quarterly observations starting from January 1st, 2006 up until July 7th, 2022.
The limited amount of data comes from Nominal Broad U.S Dollar Index (NBUSDI) only starting to be recorded by FRED in 2006.

\paragraph{Research Design and Methods}
% say statisical methods
For this paper, I plan to create a multiple linear regression model. 
For the model, my dependent variable will be Gross Domestic Product, and my independent variables will be Population (POP), Nominal Broad U.S Dollar Index (NBUSDI), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Business Sector Labor Productivity (BSLP). 
My goal is to find which independent variables are associated and can help predict the value of GDP. 
There has been much research into what impacts GDP, but I am curious to see if Nominal Broad U.S Dollar Index (NBUSDI) and  Business Sector Labor Productivity (BSLP) are successful indicators. 
My methods will help my hypothesis becuase it allows me to compare variables against one another while also testing their relationship to GDP.

\paragraph{Discussion}
I expect to find that many of my variables will have a strong relationship with GDP.
Mainly, I expect Disposable Personal Income (DPI) and Unemployment Rate (UNRATE) to have the strongest relationships since person consumption and high goverment costs impact GDP.
I am interested in testing Nominal Broad U.S Dollar Index (NBUSDI) because this varible measures the U.S. dollar compared with all other currencies. 
This variable is assocated with exports which is used when calculating GDP.
I am also interested in testing Business Sector Labor Productivity (BSLP). GDP is a measure of labor productivity, so I am expecting BSLP to have a strong relationship with GDP.

\paragraph{Conclusion}
Overall, even though there is a lot of research about what impacts GDP, my main goal is to test these methods myself. 
The purpose behind my research is to corroborate previous research while also exploring my own interest.
If my model is successful, I will be able to confirm my expectations while also indicating to economists which variables they should focus on.

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

\end{document}

### 2022-10-07 Proposal/Proposal.tex
commit #add refs
commit
commit #cite

@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity." (add bea citation) 
+It is a "comprehensive measure of U.S economic activity." \citet[]{gross domestic product | u.s. bureau of economic analysis (bea)_2022}
 GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
-(cite K.
-Hema Divya) found that exchange rates and market indexes are important factors that influence an economies GDP.
+\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP.
 They also found that inflation is highly correlated, but not a significant influencer.
@@
 
-\bibliography{../manuscript/refs}
+\bibliography{refrences}
 \bibliographystyle{chicago}

### 2022-10-07 Proposal/Proposal.tex
commit

@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity." \citet[]{gross domestic product | u.s. bureau of economic analysis (bea)_2022}
+It is a "comprehensive measure of U.S economic activity." \citet[]{gdp}
 GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 

### 2022-10-07 Proposal/Proposal.tex
commit

@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity." \citet[]{gdp}
+It is a "comprehensive measure of U.S economic activity." \citet[]{Bureau of Economic Analysis}
 GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 

### 2022-10-07 Proposal/Proposal.tex
commit

--- 2022-10-07 Proposal/Proposal.tex
@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity." \citet[]{gdp}
+It is a "comprehensive measure of U.S economic activity." \citet[]{BureauofEconomicAnalysis}
 GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 

### 2022-10-07 Proposal/Proposal.tex
commit

--- 2022-10-07 Proposal/Proposal.tex
@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity." \citet[]{gdp}
+It is a "comprehensive measure of U.S economic activity." \citet[]{bea}
 GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 

### 2022-10-07 Proposal/Proposal.tex
commit

@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity." \citet[]{bea}
+It is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
 GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
@@
 This is important becuause even though there is an abdunace of resouces avaiable about GDP, this information can change based on country, variables used, and which years your data contains. 
-Having the ability to accurately predict GDP is important because governments, corporations, and investors heavily take GDP into consideration when making decisions. (cite CFI article)
+Having the ability to accurately predict GDP is important because governments, corporations, and investors heavily take GDP into consideration when making decisions \citet[]{cfi}.
 

### 2022-10-09 Proposal/Proposal.tex
commit
commit #adding notes

@@
 
-%% preamble: Keep it clean; only include those you need
+%% preamble
 \usepackage{amsmath}
@@
 
-% for space filling
-\usepackage{lipsum}
-% highlighting hyper links
+% highlighting hyper links and refrences 
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
 
-%% meta data
+% Need to research how to properly cite websites
 
@@
 Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-It is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
-GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
+GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
+For this paper, I will focus solely on the GDP in the United States. 
 \citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP.
@@
 
+%ask if should use dif variables w more observations
 \paragraph{Data}
 My data has been collected from the Federal Reserve Economic Data (FRED) website.
-All of the datasets have been collected seperately and compiled into one dataset. 
+The data from the FRED website is collected and updated by the Research Department at the Federal Reserve Bank of St. Louis. 
+All of the datasets used in this analysis have been collected seperately and compiled into one dataset. 
 There are seven variables and sixty seven observations in this dataset. 
@@
 I expect to find that many of my variables will have a strong relationship with GDP.
-Mainly, I expect Disposable Personal Income (DPI) and Unemployment Rate (UNRATE) to have the strongest relationships since person consumption and high goverment costs impact GDP.
+Mainly, I expect Disposable Personal Income (DPI) and Unemployment Rate (UNRATE) to have the strongest relationships since personal consumption and high goverment costs impact GDP.
 I am interested in testing Nominal Broad U.S Dollar Index (NBUSDI) because this varible measures the U.S. dollar compared with all other currencies. 

### 2022-11-10 Manuscript/manuscript.tex
commit

--- 2022-10-09 Proposal/Proposal.tex
@@
 
-\title{Proposal: Influences of GDP in the U.S }
+\title{Influences of GDP in the U.S }
 \author{Ginamarie Mastrorilli\\
@@
 
+\paragraph{Abstract}
+
+\paragraph{Keywords}
+
 \paragraph{Introduction}
-%Introduction: Introducing the topic and why you have chosen this topic (3–5 lines). 
-%Mention briefly the current related research and cite relevant works.
-Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
+%  the introduction sections need to explain the importance of the topic of the paper, provide the background of the research work, and highlight the contributions of the work.
+At the end of the introduction, a roadmap, or an outline of the paper is useful in helping the readers navigating through the following sections.
+%Why does it matter?
+%What have been done?
+%What is new?
+
+% start with overview
+
+What is Gross Domestic Product? Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
 GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
-For this paper, I will focus solely on the GDP in the United States. 
-\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP.
-They also found that inflation is highly correlated, but not a significant influencer.
+There has been extensive research into GDP and what factors impact it. 
+Which factors have been researched are subjective based on those who are conducting the study.
+For this paper, we will quantify the relation between influencers of GDP.
 
-\paragraph{Specific Aims}
-%Specific aims: Formulate a research question or hypothesis in the chosen topic.
-% Describe briefly why you select such a question or hypothesis and its importance in the field (cite sources).
-With so many economic factors and data readily avaiable, which variables should economists focus on?
-When investigating U.S. Gross Domestic Product, the goal is to determine the relationship between variables and if those variables can help predict GDP.
-If a variable tends to predict the value of GDP, then economists should focus more on these independent variables when forecasting Gross Domestic Product.
-I decided to choose this topic because as an Economics minor, I have seen similar analysis, but have never had the opportunity to do this statistical analysis myself. 
-This is important becuause even though there is an abdunace of resouces avaiable about GDP, this information can change based on country, variables used, and which years your data contains. 
-Having the ability to accurately predict GDP is important because governments, corporations, and investors heavily take GDP into consideration when making decisions \citet[]{cfi}.
+\paragraph{Data}
 
-%ask if should use dif variables w more observations
-\paragraph{Data}
-My data has been collected from the Federal Reserve Economic Data (FRED) website.
-The data from the FRED website is collected and updated by the Research Department at the Federal Reserve Bank of St. Louis. 
-All of the datasets used in this analysis have been collected seperately and compiled into one dataset. 
-There are seven variables and sixty seven observations in this dataset. 
-My dependent variable is Gross Domestic Product (GDP). 
-My independent variables are Population (POP), Nominal Broad U.S Dollar Index (NBUSDI), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Business Sector Labor Productivity (BSLP).
-The dataset contains quarterly observations starting from January 1st, 2006 up until July 7th, 2022.
-The limited amount of data comes from Nominal Broad U.S Dollar Index (NBUSDI) only starting to be recorded by FRED in 2006.
+\paragraph{Methods}
 
-\paragraph{Research Design and Methods}
-% say statisical methods
-For this paper, I plan to create a multiple linear regression model. 
-For the model, my dependent variable will be Gross Domestic Product, and my independent variables will be Population (POP), Nominal Broad U.S Dollar Index (NBUSDI), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Business Sector Labor Productivity (BSLP).
-My goal is to find which independent variables are associated and can help predict the value of GDP. 
-There has been much research into what impacts GDP, but I am curious to see if Nominal Broad U.S Dollar Index (NBUSDI) and  Business Sector Labor Productivity (BSLP) are successful indicators. 
-My methods will help my hypothesis becuase it allows me to compare variables against one another while also testing their relationship to GDP.
+\paragraph{Application}
 
 \paragraph{Discussion}
-I expect to find that many of my variables will have a strong relationship with GDP.
-Mainly, I expect Disposable Personal Income (DPI) and Unemployment Rate (UNRATE) to have the strongest relationships since personal consumption and high goverment costs impact GDP.
-I am interested in testing Nominal Broad U.S Dollar Index (NBUSDI) because this varible measures the U.S. dollar compared with all other currencies. 
-This variable is assocated with exports which is used when calculating GDP.
-I am also interested in testing Business Sector Labor Productivity (BSLP). GDP is a measure of labor productivity, so I am expecting BSLP to have a strong relationship with GDP.
 
-\paragraph{Conclusion}
-Overall, even though there is a lot of research about what impacts GDP, my main goal is to test these methods myself. 
-The purpose behind my research is to corroborate previous research while also exploring my own interest.
-If my model is successful, I will be able to confirm my expectations while also indicating to economists which variables they should focus on.
+\paragraph{Appendix}
 

### 2022-11-10 Manuscript/analysis.R

@@ -1,0 +1,3 @@
+x <- 8
+x
+

### 2022-11-10 Manuscript/manuscript.tex
commit # intro

@@
 GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
+Gross Domestic Product was originally invented in the 1600's but evolved into governmental use in the 1900's. 
+GDP became a national tool to measure a countries economic activity in the 1940's after the Bretton Woods confrence in New Hampshire, US.
+At this time, Gross National Product was still a main tool to measure production, but in 1991, the United States swiched to using GDP as its main estimate. 
+GDP is calculated by
+
+$C + I + G + NX = GDP$
+
+summing private consumption, gross private investments, government investments, government spending, and the difference between exports and imports (Net Exports). 
+This equation is one that is learned in into to macroeconomics courses. 
+Calculating GDP is something that economists have
+
 There has been extensive research into GDP and what factors impact it. 
 Which factors have been researched are subjective based on those who are conducting the study.
+
+% existing works 
+\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP.
+They also found that inflation is highly correlated, but not a significant influencer.
+
+Szustak found that the relationship between power production and GDP is random. This
+
+% roadmap and contributions
+
 For this paper, we will quantify the relation between influencers of GDP.

### 2022-11-10 Manuscript/manuscript.tex
commit

@@
 At this time, Gross National Product was still a main tool to measure production, but in 1991, the United States swiched to using GDP as its main estimate. 
-GDP is calculated by
+GDP is calculated by the equation:
 
+% made centered
 $C + I + G + NX = GDP$
 
-summing private consumption, gross private investments, government investments, government spending, and the difference between exports and imports (Net Exports). 
-This equation is one that is learned in into to macroeconomics courses. 
-Calculating GDP is something that economists have
-
-There has been extensive research into GDP and what factors impact it. 
+In this equation, "(C) represents private-consumption expenditures by households and nonprofit organizations, investment (I) refers to business expenditures by businesses and home purchases by households,
+government spending (G) denotes expenditures on goods and services by the government, and net exports (NX) represents a nation’s exports minus its imports." (CITE BRITICANICA)
+This equation is one that is learned in any introduction to macroeconomics courses. 
+Calculating GDP is something that economists have accomplished and this equation is accepted in the industry. 
+What economists are now researching is what factors impact Gross Domestic Product. 
+There has been an abdunace of research in this field related to what variables are significant. 
 Which factors have been researched are subjective based on those who are conducting the study.

### 2022-11-10 Manuscript/manuscript.tex
commit

@@
 
+(cite GDP PARAdox) researches the critism behind GDP's influence in economies.
+They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare.
+Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries." (cite PARADOX)
+They also touch on how government agencies and politicians strive to avoid low GDP.
+When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (cite PARADOX)
+
 Szustak found that the relationship between power production and GDP is random. This

### 2022-11-10 Manuscript/manuscript.tex
commit

@@
 
+Kalyoncu found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia."(cite dergipark thing).
+Their research focused on the relationship between energy consumption and economic growth.
+The countries they focused their study on, Georgia, Azerbaijan and Armenia from 1995 to 2009, all faced low energy supply. 
 % roadmap and contributions
@@
 \paragraph{Data}
+%Who collected the data (source)?
+
+The economic data used in this research was collected from Federal Reserve Economic Data(FRED).
+This is an online database that is maintained by the Research Department at the Federal Reserve Bank of St.
+Louis.
+The energy data used in this research was collected from the U.S.
+Energy Information Administration website.
+The EIA "ollects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
+%How was the data collected? Sampling frame? Sampling approach?
+
+%What period or range does the data cover?
+
+%Why does the data helps answer the research question?
+
+%What exploratory analyses are done (descriptives, visualication, etc.)?
 

### 2022-11-10 Manuscript/manuscript.tex
commit

@@
 \paragraph{Data}
-%Who collected the data (source)?
+%Who collected the data (source)? How was the data collected? Sampling frame? Sampling approach? What period or range does the data cover?
 
@@
 Louis.
-The energy data used in this research was collected from the U.S.
+The variables collected from the FRED website are Gross Domestic Product (Billions of Dollars, Quarterly, Seasonally Adjusted Annual Rate), Population (Thousands, Quarterly, Not Seasonally Adjusted), Market Yield on U.S.
+Treasury Securities at 10-Year Constant Maturity, Disposable Personal Income (Billions of Dollars, Quarterly, Seasonally Adjusted Annual), Unemployment Rate (Percent, Quarterly, Seasonally Adjusted), and Business Sector: Labor Productivity (Output per Hour) for All Employed Persons.
+The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S.
 Energy Information Administration website.
-The EIA "ollects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
-%How was the data collected? Sampling frame? Sampling approach?
-
-%What period or range does the data cover?
+The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
+My independent variables are Population (POP), Business Sector Labor Productivity (BSLP), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Total Primary Energy Consumption (TPEC).
+The dependent variable is Gross Domestic Product (GDP).
+Observations are taken quarterly from January 1st, 1973 to July 1st, 2022.
 

### 2022-11-11 Manuscript/manuscript.tex
commit

@@
 
-%% preamble
 \usepackage{amsmath}
@@
 \usepackage{natbib}
+\usepackage{multirow}
 
-% highlighting hyper links and refrences 
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
-
-% Need to research how to properly cite websites
 
@@
 Treasury Securities at 10-Year Constant Maturity, Disposable Personal Income (Billions of Dollars, Quarterly, Seasonally Adjusted Annual), Unemployment Rate (Percent, Quarterly, Seasonally Adjusted), and Business Sector: Labor Productivity (Output per Hour) for All Employed Persons.
-The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S.
-Energy Information Administration website.
+
+The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S. Energy Information Administration website. 
 The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
@@
 The dependent variable is Gross Domestic Product (GDP).
-Observations are taken quarterly from January 1st, 1973 to July 1st, 2022.
+Observations are taken quarterly from January 1st, 1973 to July 1st, 2022. In this dataframe there are 199 observations from 7 variables with no missing values. 
+Summary statistics for the data is as follows
+
+\begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
+  \hline
+  \multicolumn{9}{|c|}{Summary} \\
+  \hline
+  Variable & Min. & 1st Quantile & Median & Mean & 3rd Quantile & Max. \\
+  \hline
+  TPEC & 5.669 & 6.07& 7.609 & 7.462 & 8.082 & 9.965\\
+  GDP &  1377 & 4341 & 8363 & 9962 & 14940 & 25248\\
+  POP & 211192 & 238482 & 271709 & 273195 & 30886 & 332940\\
+  TCMR & .6506 & 3.4607 & 6.1448 & 6.1156 & 8.054 & 14.8384\\
+  DPI & 968.7 & 3114.2 & 6037.2 & 7440.5 & 11171.3 & 19586.5\\
+  UNRATE & 3.6 & 5.05 & 5.867 & 6.231 & 7.3 & 12.967\\
+  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96\\
+  \hline
+ \end{tabular}
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 \usepackage{multirow}
+\usepackage{setspace}
+\usepackage[colorlinks=true, citecolor=blue]{hyperref}
 
-\usepackage[colorlinks=true, citecolor=blue]{hyperref}
+\doublespacing
 
@@
 
-% made centered
-$C + I + G + NX = GDP$
+\begin{equation}
+C + I + G + NX = GDP
+\end{equation}
 
@@
 
+To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
+Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
+Multiple linear regrssion is a continuation of simple linear regression. 
+For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
+The general form of the multiple linear regression model is as follows:
+
+\begin{equation}
+  Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + ... + \beta_n X_n + \epsilon
+\end{equation}
+
+In this equation, Y is an outcomes that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
+$\beta_n X_n$ is the last regression coefficent for the final variable in the model.
+$\epsilon$ represents how much variation there is in our estimate for the dependent variable, or otherwise known as model error.
+
 \paragraph{Application}
+
+When applying multiple linear regression to the data set, all independent variables were included in the intital model.
+The model was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the traing dataset.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{AVP1}
+\end{figure}
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 \paragraph{Methods} 
-
 To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
@@
 
-In this equation, Y is an outcomes that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
+In this equation, Y is an outcome that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
 $\beta_n X_n$ is the last regression coefficent for the final variable in the model.
 $\epsilon$ represents how much variation there is in our estimate for the dependent variable, or otherwise known as model error.
+
+For this research, the data will be split into two datasets, a training set and a validation set. 
+This procedure is used to measure the performance of the models built. 
+The training dataset is used to fit the desired model, whereas the validation dataset is used to evaluate the fit of that desired model. 
+For this purpose, the data will be split into .8 train and .2 into validation.
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 The economic data used in this research was collected from Federal Reserve Economic Data(FRED). 
-This is an online database that is maintained by the Research Department at the Federal Reserve Bank of St.
-Louis.
+This is an online database that is maintained by the Research Department at the Federal Reserve Bank of St. Louis. 
 The variables collected from the FRED website are Gross Domestic Product (Billions of Dollars, Quarterly, Seasonally Adjusted Annual Rate), Population (Thousands, Quarterly, Not Seasonally Adjusted), Market Yield on U.S.
@@
 The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
-My independent variables are Population (POP), Business Sector Labor Productivity (BSLP), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Total Primary Energy Consumption (TPEC).
+
+In the original dataframe there are 199 observations from 7 variables with no missing values.
+Observations are complied quarterly from January 1st, 1973 to July 1st, 2022.  
+For this paper, the original dataset will be split into two datasets, a training set and a validation set. 
+This procedure is used to measure the performance of the models built. 
+The training dataset is used to fit the desired model, whereas the validation dataset is used to evaluate the fit of that desired model. 
+For this purpose, the data will be split into .8 train and .2 into validation.
+The independent variables are Population (POP), Business Sector Labor Productivity (BSLP), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Total Primary Energy Consumption (TPEC).
 The dependent variable is Gross Domestic Product (GDP).
-Observations are taken quarterly from January 1st, 1973 to July 1st, 2022. In this dataframe there are 199 observations from 7 variables with no missing values. 
-Summary statistics for the data is as follows
+Summary statistics for the training dataset are as follows:
 
+%need to fix formatting
 \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
@@
 
-For this research, the data will be split into two datasets, a training set and a validation set. 
-This procedure is used to measure the performance of the models built. 
-The training dataset is used to fit the desired model, whereas the validation dataset is used to evaluate the fit of that desired model. 
-For this purpose, the data will be split into .8 train and .2 into validation.
-
 \paragraph{Application}
@@
 When applying multiple linear regression to the data set, all independent variables were included in the intital model.
-The model was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the traing dataset.
+The model was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the training dataset.
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 \usepackage{setspace}
+\usepackage{float}
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
@@
 
+% explain VIF and AV plots
+
 \paragraph{Application}
@@
 When applying multiple linear regression to the data set, all independent variables were included in the intital model.
-The model was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the training dataset.
+Model 1 was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the training dataset. 
+The equation used for this model is as follows:
+
+\begin{equation}
+  GDP = \beta_0 + \beta_1 TPEC + \beta_2 TCMR+ \beta_3 DPI + \beta_4 UNRATE + \beta_5 BSPL
+\end{equation}
+
+Summary statistics for this model are as follows:
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width = \textwidth]{mod1output}
+  \caption{This figure shows the output from R for the summary statistics for Model 1}
+\end{figure}
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
   \centering
-  \includegraphics[width = \textwidth]{mod1output}
+  \includegraphics[scale = .5]{mod1output}
   \caption{This figure shows the output from R for the summary statistics for Model 1}
 \end{figure}
+
+From the output of Model 1, it concludes that the model is useful.
+This is because the P-Value of the F-Test is less than $2.2 * 10^{-16}$
+The variables TCMR, DPI, UNRATE and BSLP are significant in this model, whereas the variables TPEC and POP are not significantly differnt from zero at the five percent level of significance.  
+The R-Squared value indicates that this model is a good fit since 99.73\% of the variablity in the data is explated by the model. 
+Model 1 found significant relationships between the frequency of GDP and the variables TCMR, DPI, UNRATE and BSLP. 
+This is due to P-Value associated with these variables is less than .001. 
+Specifically it found a 86.87\% increase in the frequency of GDP for every 1\% increase in TCMR, a 86.99\% increase in the frequency of GDP for every 1\% increase in DPI, a -19.37\% decrease in the frequency of GDP for every 1\% increase in UNRATE, and a 84.59\% increase in the frequency of GDP for every 1\% increase in BSLP.
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 
+"A strong linear relationship in the added variable plot indicates the increased importance of the contribution of X to the model already containing the other predictors.
+
 \paragraph{Application}
@@
 
+The Added Variable Plots for the model are as follows:
+
 \begin{figure}[h]
@@
   \includegraphics[width=\textwidth]{AVP1}
+  \caption{This figure shows the AV Plots for the variables included in Model 1}
 \end{figure}

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 \begin{equation}
-  GDP = \beta_0 + \beta_1 TPEC + \beta_2 TCMR+ \beta_3 DPI + \beta_4 UNRATE + \beta_5 BSPL
+  GDP = \beta_0 + \beta_1 TPEC + \beta_2 TCMR+ \beta_3 DPI + \beta_4 UNRATE + \beta_5 BSPL +\beta_6 POP
 \end{equation}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
   \centering
-  \includegraphics[width=\textwidth]{AVP1}
+  \includegraphics[scale = .5]{AVP1}
   \caption{This figure shows the AV Plots for the variables included in Model 1}
+\end{figure}
+
+From the output above, it can be concluded that there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP.
+A weak linear relationship is show fromthe varibles TPEC and POP with GDP. 
+This output confirms that the relationship between TPEC and POP with GDP are not significant in this model.
+
+For the second model, the non significant variables from Model 1 are removed. 
+Model 1 was built using the independent variables TCMR, DPI, UNRATE and BSLP from the training dataset. 
+The equation used for Model 2 is as follows:
+
+\begin{equation}
+  GDP = \beta_0 + \beta_1TCMR+ \beta_2 DPI + \beta_3 UNRATE + \beta_4 BSPL
+\end{equation}
+
+Summary statistics for Model 2 are as follows:
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .5]{mod2output}
+  \caption{This figure shows the output from R for the summary statistics for Model 2}
 \end{figure}

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 From the output of Model 1, it concludes that the model is useful.
-This is because the P-Value of the F-Test is less than $2.2 * 10^{-16}$
-The variables TCMR, DPI, UNRATE and BSLP are significant in this model, whereas the variables TPEC and POP are not significantly differnt from zero at the five percent level of significance.  
+This is because the P-Value of the F-Test is less than $2.2 * 10^{-16}$.
+The variables TCMR, DPI, UNRATE and BSLP are significant in this model, whereas the variables TPEC and POP are not significantly differnt from zero at the 5\% level of significance.  
 The R-Squared value indicates that this model is a good fit since 99.73\% of the variablity in the data is explated by the model. 
@@
 
+From the output above of Model 2, it concludes that the model is useful.
+This is because the P-Value of the F-Test is less than $2.2 * 10^{-16}$.
+All of the variables in this model (TCMR, DPI, UNRATE and BSLP) are significant at the 5\% level of significance.
+The R-Squared value indicates that this model is a good fit since 99.72\% of the variablity in the data is explated by the model. 
+Model 2 found significant relationships between the frequency of GDP and the variables TCMR, DPI, UNRATE and BSLP. 
+This is due to P-Value associated with these variables is less than .001. 
+Specifically it found a 94.37\% increase in the frequency of GDP for every 1\% increase in TCMR, a 85.84\% increase in the frequency of GDP for every 1\% increase in DPI, a -20.65\% decrease in the frequency of GDP for every 1\% increase in UNRATE, and a 10.81\% increase in the frequency of GDP for every 1\% increase in BSLP.
+
+The Added-Variable Plots for variables included in Model 2 are as follows:
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .5]{AVP2}
+  \caption{This figure shows the AV Plots for the variables included in Model 2}
+\end{figure}
+
 \paragraph{Discussion}

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 \usepackage{natbib}
+\usepackage{tabularx}
 \usepackage{multirow}
+\usepackage{multicol}
 \usepackage{setspace}
@@
 
-%need to fix formatting
-\begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
+\begin{tabular}{ |p{2cm}||p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| }
   \hline
-  \multicolumn{9}{|c|}{Summary} \\
+  \multicolumn{7}{|c|}{Summary} \\
   \hline
-  Variable & Min. & 1st Quantile & Median & Mean & 3rd Quantile & Max. \\
+  Variable & Min. & 1st Q & Median & Mean & 3rd Q & Max. \\
   \hline
@@
   UNRATE & 3.6 & 5.05 & 5.867 & 6.231 & 7.3 & 12.967\\
-  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96\\
+  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96 & 116.10\\
   \hline
@@
 
+From the output produced in the Added-Variable Plots from Model 2, it confirms there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP.
+
 \paragraph{Discussion}

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 In this equation, "(C) represents private-consumption expenditures by households and nonprofit organizations, investment (I) refers to business expenditures by businesses and home purchases by households,
-government spending (G) denotes expenditures on goods and services by the government, and net exports (NX) represents a nation’s exports minus its imports." (CITE BRITICANICA)
+government spending (G) denotes expenditures on goods and services by the government, and net exports (NX) represents a nation’s exports minus its imports" \citet[]{brit}.
 This equation is one that is learned in any introduction to macroeconomics courses. 
@@
 
-(cite GDP PARAdox) researches the critism behind GDP's influence in economies.
+\citet{van2009gdp} researches the critism behind GDP's influence in economies.
 They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare.
-Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries." (cite PARADOX)
+Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries"\citet[]{van2009gdp}.
 They also touch on how government agencies and politicians strive to avoid low GDP.
-When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (cite PARADOX)
+When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power\citet[]{van2009gdp}.
 
@@
 
-\begin{tabular}{ |p{2cm}||p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| }
+\begin{center}
+\begin{tabular}{ |p{1.75cm}||p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}| }
   \hline
@@
 \end{tabular}
+\end{center}
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
   What is Gross Domestic Product? Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
+GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" (\citet[]{bea}).
 Gross Domestic Product was originally invented in the 1600's but evolved into governmental use in the 1900's. 
@@
 They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare.
-Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries"\citet[]{van2009gdp}.
+Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries" (\citet[]{van2009gdp}).
 They also touch on how government agencies and politicians strive to avoid low GDP.
-When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power\citet[]{van2009gdp}.
+When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (\citet[]{van2009gdp}).
 

### 2022-11-12 Manuscript/manuscript.tex
commit

@@
 
-\paragraph{Abstract}
+\section*{Abstract}
 
-\paragraph{Keywords}
+\section*{Keywords}
 
-\paragraph{Introduction}
+\section*{Introduction}
 %  the introduction sections need to explain the importance of the topic of the paper, provide the background of the research work, and highlight the contributions of the work.
@@
 
-Szustak found that the relationship between power production and GDP is random. This
+\citet{szustak2021relationship} found that the relationship between power production and GDP is random. This
 
-Kalyoncu found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia."(cite dergipark thing).
-Their research focused on the relationship between energy consumption and economic growth.
+\citet{kalyoncu2013causality} found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia." Their research focused on the relationship between energy consumption and economic growth.
 The countries they focused their study on, Georgia, Azerbaijan and Armenia from 1995 to 2009, all faced low energy supply.
-% roadmap and contributions
 
@@
 
-\paragraph{Data}
+\section*{Data}
 %Who collected the data (source)? How was the data collected? Sampling frame? Sampling approach? What period or range does the data cover?
@@
 
-\paragraph{Methods} 
+\section*{Methods}
 To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
@@
 
-\paragraph{Application}
+\section*{Application}
 
@@
 
-\paragraph{Discussion}
-
-\paragraph{Appendix}
+\section*{Discussion}
 

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 \section*{Methods}
-To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
+To investigate which factors influence Gross Domestic Product, Ordinary Least Squares Regressiion will be used. 
 Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
-Multiple linear regrssion is a continuation of simple linear regression. 
-For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
-The general form of the multiple linear regression model is as follows:
+Ordinary Least Squares Regressiion is a continuation of simple linear regression. 
+For this model, there must be one or more independent predictors that are used to predict one dependent variable. 
+The general form of the OLS regression model is as follows:
 
@@
 
+OLS Regression Assumptions:
+- normality
+- heteroscedacity
+
 % explain VIF and AV plots
@@
 
-When applying multiple linear regression to the data set, all independent variables were included in the intital model.
+When applying OLS regression to the data set, all independent variables were included in the intital model.
 Model 1 was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the training dataset. 
@@
 The variables TCMR, DPI, UNRATE and BSLP are significant in this model, whereas the variables TPEC and POP are not significantly differnt from zero at the 5\% level of significance.  
-The R-Squared value indicates that this model is a good fit since 99.73\% of the variablity in the data is explated by the model. 
+The Multiple R-Squared value indicates that this model is a good fit since 99.73\% of the variablity in the data is explated by the model. 
 Model 1 found significant relationships between the frequency of GDP and the variables TCMR, DPI, UNRATE and BSLP. 
@@
 This output confirms that the relationship between TPEC and POP with GDP are not significant in this model.
+
+To check the assumptions of homoscedacity a residuals vs. fitted plot is shown.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .5]{res1}
+  \caption{This figure shows the Residuals vs. Fitted plot for Model 1}
+\end{figure}
+
+From this plot, the assumption of homoscedacity is questionable. 
+The residuals do not appear to be randomly scattered throughout the entire plot, and there could be a noticle pattern. 
+This warrents further invesigation.
+
+Next, the assumption of normality will be checked using a Q-Q Plot.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .5]{norm1}
+  \caption{This figure shows the Q-Q Plot for Model 1}
+\end{figure}
+
+From this plot, the assumption of normality is met. 
+The points fall along the line at a rough 45 degree angle. 
+There is a few stray points, but not enough concern that warrents futer invesigation.
+Therefore, the normality assumption is met.
 
@@
 
+Next, the validation data will be applied to Model 1 and Model 2.
+
 \section*{Discussion}
+
+- violate homoscedacty assumption
 

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
   \centering
-  \includegraphics[scale = .5]{res1}
+  \includegraphics[scale = .35]{res1}
   \caption{This figure shows the Residuals vs. Fitted plot for Model 1}
@@
   \centering
-  \includegraphics[scale = .5]{norm1}
+  \includegraphics[scale = .35]{norm1}
   \caption{This figure shows the Q-Q Plot for Model 1}
@@
 
+To check the assumptions of homoscedacity a residuals vs. fitted plot is shown.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .35]{res2}
+  \caption{This figure shows the Residuals vs. Fitted plot for Model 2}
+\end{figure}
+
+From this plot, the assumption of homoscedacity is questionable
+The residuals do not appear to be randomly scattered throughout the entire plot, and there could be a noticle pattern in some parts of the plot. 
+This warrents further invesigation.
+
+Next, the assumption of normality will be checked using a Q-Q Plot.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .35]{norm2}
+  \caption{This figure shows the Q-Q Plot for Model 2}
+\end{figure}
+
+From this plot, the assumption of normality is met. 
+The points fall along the line at a rough 45 degree angle. 
+There is a few stray points, but not enough concern that warrents futer invesigation.
+Therefore, the normality assumption is met.
+
 Next, the validation data will be applied to Model 1 and Model 2.
+
+The summary statistics for Model 1 application with Validation data are as follows:
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .35]{mod1v}
+  \caption{This figure shows the summary statistics for Model 1 application to the validation dataset.}
+\end{figure}
+
+The summary statistics for Model 2 application with Validation data are as follows:
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = .35]{mod2v}
+  \caption{This figure shows the summary statistics for Model 2 application to the validation dataset.}
+\end{figure}
 

### 2022-11-14 Manuscript/manuscript.tex
commit # spacing

@@
 
-\section*{Keywords}
-
 \section*{Introduction}
-%  the introduction sections need to explain the importance of the topic of the paper, provide the background of the research work, and highlight the contributions of the work.
-At the end of the introduction, a roadmap, or an outline of the paper is useful in helping the readers navigating through the following sections.
-%Why does it matter?
-%What have been done?
-%What is new?
-
-% start with overview
-
 What is Gross Domestic Product? Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
@@
 GDP is calculated by the equation: 
-
 \begin{equation}
@@
 \end{equation}
-
 In this equation, "(C) represents private-consumption expenditures by households and nonprofit organizations, investment (I) refers to business expenditures by businesses and home purchases by households,
@@
 
-% existing works 
 \citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP. 
 They also found that inflation is highly correlated, but not a significant influencer.  
-
 \citet{van2009gdp} researches the critism behind GDP's influence in economies.
@@
 When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (\citet[]{van2009gdp}).
-
 \citet{szustak2021relationship} found that the relationship between power production and GDP is random. This 
-
 \citet{kalyoncu2013causality} found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia." Their research focused on the relationship between energy consumption and economic growth.
@@
 For this paper, we will quantify the relation between influencers of GDP. 
+The main focus is to test whether energy consumption has a significant relationship to Gross Domestic Product. 
+Since energy data is readily avaiable on a monthly basis, this could be a factor economists use to predict GDP on a monthly scale.
 
 \section*{Data}
-%Who collected the data (source)? How was the data collected? Sampling frame? Sampling approach? What period or range does the data cover?
-
 The economic data used in this research was collected from Federal Reserve Economic Data(FRED). 
@@
 Summary statistics for the training dataset are as follows:
-
 \begin{center}
@@
 
-%Why does the data helps answer the research question?
-
-%What exploratory analyses are done (descriptives, visualication, etc.)?
-
 \section*{Methods}
@@
 Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
+
 Ordinary Least Squares Regressiion is a continuation of simple linear regression. 
@@
 The general form of the OLS regression model is as follows: 
-
 \begin{equation}
@@
 \end{equation}
-
 In this equation, Y is an outcome that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
@@
 % explain VIF and AV plots 
-
+AV Plors will also be ised in this analysis to 
 "A strong linear relationship in the added variable plot indicates the increased importance of the contribution of X to the model already containing the other predictors.
@@
 \section*{Application}
-
 When applying OLS regression to the data set, all independent variables were included in the intital model.
@@
 The equation used for this model is as follows:
-
 \begin{equation}
@@
 \end{equation}
-
 Summary statistics for this model are as follows:
-
 \begin{figure}[H]
@@
 \end{figure}
-
 From the output of Model 1, it concludes that the model is useful.
@@
 Specifically it found a 86.87\% increase in the frequency of GDP for every 1\% increase in TCMR, a 86.99\% increase in the frequency of GDP for every 1\% increase in DPI, a -19.37\% decrease in the frequency of GDP for every 1\% increase in UNRATE, and a 84.59\% increase in the frequency of GDP for every 1\% increase in BSLP.
-
 The Added Variable Plots for the model are as follows:
-
 \begin{figure}[H]
@@
 \end{figure}
-
 From the output above, it can be concluded that there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP.
@@
 This output confirms that the relationship between TPEC and POP with GDP are not significant in this model. 
-
 To check the assumptions of homoscedacity a residuals vs. fitted plot is shown.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 From this plot, the assumption of homoscedacity is questionable. 
 The residuals do not appear to be randomly scattered throughout the entire plot, and there could be a noticle pattern. 
-This warrents further invesigation.
-
-Next, the assumption of normality will be checked using a Q-Q Plot.
-
+This warrents further invesigation. Next, the assumption of normality will be checked using a Q-Q Plot. 
 \begin{figure}[H]
@@
 \end{figure}
-
 From this plot, the assumption of normality is met. 
@@
 The equation used for Model 2 is as follows:
-
 \begin{equation}
@@
 \end{equation}
-
 Summary statistics for Model 2 are as follows:
-
 \begin{figure}[H]
@@
 \end{figure}
-
 From the output above of Model 2, it concludes that the model is useful.
@@
 Specifically it found a 94.37\% increase in the frequency of GDP for every 1\% increase in TCMR, a 85.84\% increase in the frequency of GDP for every 1\% increase in DPI, a -20.65\% decrease in the frequency of GDP for every 1\% increase in UNRATE, and a 10.81\% increase in the frequency of GDP for every 1\% increase in BSLP.
-
 The Added-Variable Plots for variables included in Model 2 are as follows: 
-
 \begin{figure}[H]
@@
 \end{figure}
-
 From the output produced in the Added-Variable Plots from Model 2, it confirms there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP. 
-
 To check the assumptions of homoscedacity a residuals vs. fitted plot is shown.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 From this plot, the assumption of homoscedacity is questionable
@@
 This warrents further invesigation. 
-
 Next, the assumption of normality will be checked using a Q-Q Plot. 
-
 \begin{figure}[H]
@@
 Next, the validation data will be applied to Model 1 and Model 2. 
-
 The summary statistics for Model 1 application with Validation data are as follows: 
-
 \begin{figure}[H]
@@
 \end{figure}
-
 The summary statistics for Model 2 application with Validation data are as follows: 
-
 \begin{figure}[H]

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 
-% explain VIF and AV plots 
+% explain AV Plots and AIC test
 AV Plors will also be ised in this analysis to 
@@
   \centering
-  \includegraphics[scale = .5]{mod1output}
+  \includegraphics[scale = .35]{mod1output}
   \caption{This figure shows the output from R for the summary statistics for Model 1}
@@
   \centering
-  \includegraphics[scale = .5]{AVP1}
+  \includegraphics[scale = .35]{AVP1}
   \caption{This figure shows the AV Plots for the variables included in Model 1}
@@
   \centering
-  \includegraphics[scale = .5]{mod2output}
+  \includegraphics[scale = .35]{mod2output}
   \caption{This figure shows the output from R for the summary statistics for Model 2}
@@
   \centering
-  \includegraphics[scale = .5]{AVP2}
+  \includegraphics[scale = .35]{AVP2}
   \caption{This figure shows the AV Plots for the variables included in Model 2}
@@
 
+Next, and AIC test will be applied to Model 1 and Model 2 application to validation data. 
+This tested resulted in Model 1 reciving and AIC of 559.5405, and Model 2 557.1234. 
+Since Model 2 recived a lower AIC it has the most adequate fit with the least variables when built using validation data. 
+The regression equation results are as follows: 
+\begin{equation}
+  GDP = -919.82242+50.18851(TCMR)+1.20921(DPI)-81.67410(UNRATE)+28.06281(BSPL)
+\end{equation}
+
 \section*{Discussion}

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 
-\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP. 
-They also found that inflation is highly correlated, but not a significant influencer.  
-\citet{van2009gdp} researches the critism behind GDP's influence in economies.
+\citet{divya2014study} found that Exchange rate, Sensex and Balance of Payment reflected by current and capital account balance are important factors that influence India’s GDP. 
+Using correlation and ANOVA, they also found that inflation is highly correlated, but not a significant influencer. 
+The main purpose of their study is to identify key signals for an economy before a crisis occurs.
+
+\citet{van2009gdp} researches the criticism behind GDP's influence in economies. 
 They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare.
-Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries" (\citet[]{van2009gdp}).
+Since GDP is a global indicator 'The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries.'(\citet[]{van2009gdp})
 They also touch on how government agencies and politicians strive to avoid low GDP.
-When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power (\citet[]{van2009gdp}).
-\citet{szustak2021relationship} found that the relationship between power production and GDP is random. This 
-\citet{kalyoncu2013causality} found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia." Their research focused on the relationship between energy consumption and economic growth.
-The countries they focused their study on, Georgia, Azerbaijan and Armenia from 1995 to 2009, all faced low energy supply.
+When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power(\citet[]{van2009gdp}).
 
-For this paper, we will quantify the relation between influencers of GDP. 
+\citet{szustak2021relationship} investigated the possible relationship between energy production and GDP growth. 
+Their goal was to discover the direction of the relationship if one exists. 
+found that the relationship between power production and GDP is random. 
+The study found that there is not a relationship between energy production and GDP. 
+Even though in some counties the relationship was stronger, they concluded that the relationship was random.
+
+\citet{kalyoncu2013causality} focused on the relationship between energy consumption and economic growth in Georgia, Azerbaijan and Armenia from 1995 to 2009. 
+Using the Engle-Granger cointegration and Granger causality tests, they investigated the direction of causality for the purpose of informing policy makers. 
+Their research found that there is `unidirectional causality from per capita GDP to per capita energy consumption for Armenia.' (\citet[]{kalyoncu2013causality}) 
+The countries they focused their study on all faced low energy supply which is a factor that must be taken into account.
+
+This paper strives to quantify the relation between influencers of GDP. 
 The main focus is to test whether energy consumption has a significant relationship to Gross Domestic Product. 
-Since energy data is readily avaiable on a monthly basis, this could be a factor economists use to predict GDP on a monthly scale.
+This will be conducted using the variable Total Primary Energy Consumption. 
+Since energy data is readily available on a monthly basis, this indicator could be used by economists to predict GDP on a monthly scale. 
+The goal is to be able to identify signals of crucial moments to allow policy makers to make more informed decisions.
 

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 \section*{Abstract}
+This study makes an attempt to determine the influence of specific economic factors namely Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption on United States GDP.
+The data is collected from Federal Reserve Bank of St. Louis  and the U.S. Energy Information Administration from the period of January 1st, 1973 to July 1st, 2022. 
+This study’s scope is limited to these listed variables. 
+Ordinary Least Squares Regression is used to analyze the relationship between GDP and these variables. 
+The main variable of interest is Total Primary Energy Consumption. 
+The study revealed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rateare factors that significantly predict GDP of the United States.
+There was no significant relationship shown between Total Primary Energy Consumption and GDP in the United States based off of this study.
 

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 \section*{Discussion}
-
-- violate homoscedacty assumption
+In practice, there are many economic indicators that impact GDP. 
+There is no unique set of factors discovered yet that predict GDP. 
+This paper showed that TCMR, DPI, UNRATE, and BSPL have a significant relationship with GDP.
+These variables were selected with subjectivity, and this is important to take into consideration. 
+This paper did not show any significant relationship between Total Primary Energy Consumption and GDP in the United States. 
+It is also important to consider that the homoscedacy assumption of OLS Regression is questionable in this paper. 
+For future studies, to limit this violation the data could be transformed.
+This research is a introductory study into the relationship between energy consumption and economic growth. 
+This could be a useful start point for economic developers to identify signals of crucial moments to allow policy makers to make more informed decisions.
 

### 2022-11-14 Data/code.Rmd
commit #add code

```{r}
data <- as.data.frame(data)

str(data)
```

# to split into traiing and test

```{r}
smp_size <- floor(.80 * nrow(data))
set.seed(123)
train_ind <- sample(seq_len(nrow(data)), size = smp_size)

training <- data[train_ind, ]
validation <- data[-train_ind, ]

summary(training)
```

# Model 1
```{r}
fit1 <- lm(GDP ~ TPEC + POP + TCMR + DPI + UNRATE + BSLP, data = training)

summary(fit1)
```

```{r}
library(car)

avPlots(fit1)
```

```{r}
res1 <- resid(fit1)
plot(fitted(fit1), res1)
abline(0,0)
```

```{r}
qqnorm(res1)
qqline(res1)
```

## Model 2 
```{r}
fit2 <- lm(GDP ~  + TCMR + DPI + UNRATE + BSLP, data = training)

summary(fit2)
```

```{r}
avPlots(fit2)
```
```{r}
res2 <- resid(fit2)
plot(fitted(fit2), res2)
abline(0,0)
```

```{r}
qqnorm(res2)
qqline(res2)
```

# Validation

```{r}
fit1v <- lm(GDP ~ TPEC + POP + TCMR + DPI + UNRATE + BSLP, data = validation)

summary(fit1v)
```

```{r}
fit2v <- lm(GDP ~  + TCMR + DPI + UNRATE + BSLP, data = validation)

summary(fit2v)
```

```{r}
AIC(fit1v, fit2v)
```

### 2022-11-14 Manuscript/analysis.R
commit

@@ -1,3 +1,0 @@
-x <- 8
-x
-

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 What is Gross Domestic Product? Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
-GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" (\citet[]{bea}).
+GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
 Gross Domestic Product was originally invented in the 1600's but evolved into governmental use in the 1900's. 
@@
 They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare.
-Since GDP is a global indicator 'The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries.'(\citet[]{van2009gdp})
+Since GDP is a global indicator 'The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries'\citet[]{van2009gdp}.
 They also touch on how government agencies and politicians strive to avoid low GDP.
-When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power(\citet[]{van2009gdp}).
+When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power\citet[]{van2009gdp}.
 
 \citet{szustak2021relationship} investigated the possible relationship between energy production and GDP growth. 
-Their goal was to discover the direction of the relationship if one exists. 
-found that the relationship between power production and GDP is random. 
-The study found that there is not a relationship between energy production and GDP. 
-Even though in some counties the relationship was stronger, they concluded that the relationship was random.
+Their goal was to discover the direction of the relationship, if one exists. 
+The study found that there is not a significant relationship between energy production and GDP. 
+Even though in some countries the relationship was stronger, they concluded that the relationship was random.
 
@@
 Using the Engle-Granger cointegration and Granger causality tests, they investigated the direction of causality for the purpose of informing policy makers. 
-Their research found that there is `unidirectional causality from per capita GDP to per capita energy consumption for Armenia.' (\citet[]{kalyoncu2013causality}) 
-The countries they focused their study on all faced low energy supply which is a factor that must be taken into account.
+Their research found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia" \citet[]{kalyoncu2013causality}.
+The countries they focused their study on all faced low energy supply, which is a factor that must be taken into account.
 
@@
 Since energy data is readily available on a monthly basis, this indicator could be used by economists to predict GDP on a monthly scale. 
-The goal is to be able to identify signals of crucial moments to allow policy makers to make more informed decisions.
+The goal is to be able to identify signals of crucial moments in the economy to allow policy makers to make more informed decisions.
 
@@
 The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S. Energy Information Administration website. 
-The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."(EIA)
+The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."\citet[]{eia}.
 
@@
 $\epsilon$ represents how much variation there is in our estimate for the dependent variable, or otherwise known as model error.
-
-OLS Regression Assumptions:
-- normality
-- heteroscedacity
-
-% explain AV Plots and AIC test
-AV Plors will also be ised in this analysis to 
-"A strong linear relationship in the added variable plot indicates the increased importance of the contribution of X to the model already containing the other predictors.
 

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S. Energy Information Administration website. 
-The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."\citet[]{eia}.
+The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment." \citet[]{eia}.
 

### 2022-11-14 Manuscript/manuscript.tex
commit

--- 2022-11-14 Manuscript/manuscript.tex
@@
 The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S. Energy Information Administration website. 
-The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."\citet[]{eia}.
+The EIA collects and analyzes data to promote energy information.
+Their goal is to promote effective policy decisions, efficient markets, and to increase the public's understanding of energy and its influence on the economy.
 

### 2022-11-14 Manuscript/manuscript.tex
commit

@@
 The training dataset is used to fit the desired model, whereas the validation dataset is used to evaluate the fit of that desired model. 
-For this purpose, the data will be split into .8 train and .2 into validation.
+For this purpose, the data will be split 80\% train and 20\% into validation.
 The independent variables are Population (POP), Business Sector Labor Productivity (BSLP), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Total Primary Energy Consumption (TPEC).
@@
   \centering
-  \includegraphics[scale = .35]{AVP1}
+  \includegraphics[scale = .5]{AVP1}
   \caption{This figure shows the AV Plots for the variables included in Model 1}
@@
 From the output above, it can be concluded that there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP.
-A weak linear relationship is show fromthe varibles TPEC and POP with GDP. 
+A weak linear relationship is show from the varibles TPEC and POP with GDP. 
 This output confirms that the relationship between TPEC and POP with GDP are not significant in this model. 
@@
   \centering
-  \includegraphics[scale = .35]{res1}
+  \includegraphics[scale = .45]{res1}
   \caption{This figure shows the Residuals vs. Fitted plot for Model 1}
@@
 The points fall along the line at a rough 45 degree angle. 
-There is a few stray points, but not enough concern that warrents futer invesigation.
+There are a few stray points, but not enough concern that warrents futer invesigation.
 Therefore, the normality assumption is met.
@@
 For the second model, the non significant variables from Model 1 are removed. 
-Model 1 was built using the independent variables TCMR, DPI, UNRATE and BSLP from the training dataset. 
+Model 2 was built using the independent variables TCMR, DPI, UNRATE and BSLP from the training dataset. 
 The equation used for Model 2 is as follows:
@@
   \centering
-  \includegraphics[scale = .35]{AVP2}
+  \includegraphics[scale = .45]{AVP2}
   \caption{This figure shows the AV Plots for the variables included in Model 2}
@@
   \centering
-  \includegraphics[scale = .35]{res2}
+  \includegraphics[scale = .3]{res2}
   \caption{This figure shows the Residuals vs. Fitted plot for Model 2}
@@
 This paper showed that TCMR, DPI, UNRATE, and BSPL have a significant relationship with GDP.
-These variables were selected with subjectivity, and this is important to take into consideration. 
+These variables were selected with author subjectivity, and this is important to take into consideration. 
 This paper did not show any significant relationship between Total Primary Energy Consumption and GDP in the United States. 
-It is also important to consider that the homoscedacy assumption of OLS Regression is questionable in this paper. 
+It is also important to consider that the homoscedacity assumption of OLS Regression is questionable in this paper. 
 For future studies, to limit this violation the data could be transformed.

### 2022-12-08 Manuscript/manuscript.tex
commit
commit #intro

@@
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
+\usepackage [english]{babel}
+\usepackage [autostyle, english = american]{csquotes}
+\MakeOuterQuote{"}
 
@@
 \section*{Abstract}
-This study makes an attempt to determine the influence of specific economic factors namely Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption on United States GDP.
-The data is collected from Federal Reserve Bank of St. Louis  and the U.S. Energy Information Administration from the period of January 1st, 1973 to July 1st, 2022. 
+This study makes an attempt to determine the influence of specific economic factors namely Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption on United States Gross Domestic Product.
+The data is collected from the Federal Reserve Bank of St. Louis and the U.S. Energy Information Administration from the period of January 1st, 1973 to July 1st, 2022. 
 This study’s scope is limited to these listed variables. 
@@
 This equation is one that is learned in any introduction to macroeconomics courses. 
-Calculating GDP is something that economists have accomplished and this equation is accepted in the industry. 
+Calculating GDP is a tool that economists have mastered and this equation is widely accepted in the industry. 
 What economists are now researching is what factors impact Gross Domestic Product. 

### 2022-12-09 Manuscript/manuscript.tex
commit
commit #discussion

@@
 
-\title{Influences of GDP in the U.S }
+\title{Influences of GDP in the United States }
 \author{Ginamarie Mastrorilli\\
@@
 This study makes an attempt to determine the influence of specific economic factors namely Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption on United States Gross Domestic Product.
-The data is collected from the Federal Reserve Bank of St. Louis and the U.S. Energy Information Administration from the period of January 1st, 1973 to July 1st, 2022. 
+The data is collected from the Federal Reserve Bank of St.Louis and the U.S. Energy Information Administration from the period of January 1st, 1973 to July 1st, 2022. 
 This study’s scope is limited to these listed variables. 
@@
 The main variable of interest is Total Primary Energy Consumption. 
-The study revealed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rateare factors that significantly predict GDP of the United States.
+The study revealed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rate are factors that significantly predict GDP of the United States.
 There was no significant relationship shown between Total Primary Energy Consumption and GDP in the United States based off of this study.
@@
 They compare the understanding that even though GDP can influence economically relevant decisions, it does not factor in social welfare.
-Since GDP is a global indicator 'The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries'\citet[]{van2009gdp}.
+Since GDP is a global indicator "The importance of GDP information for firms, investors and citizens/consumers is illustrated by the media – television, radio, newspapers, financial and other magazines, and internet – informing us on a daily basis about the status of our national GDP, both over time and in comparison with other countries" \citet[]{van2009gdp}.
 They also touch on how government agencies and politicians strive to avoid low GDP.
-When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power\citet[]{van2009gdp}.
+When GDP is low, this can lead to negative voter response, and less public expenditures, which are both fatal prospects for those in power \citet[]{van2009gdp}.
 
@@
 Their research found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia" \citet[]{kalyoncu2013causality}.
-The countries they focused their study on all faced low energy supply, which is a factor that must be taken into account.
+The countries they focused their study on all faced low energy supply, which is a factor that must be taken into account when analyzing their study.
 
@@
 \section*{Data}
-The economic data used in this research was collected from Federal Reserve Economic Data(FRED). 
-This is an online database that is maintained by the Research Department at the Federal Reserve Bank of St. Louis. 
+The economic data used in this research was collected from Federal Reserve Economic Data (FRED). 
+This is an online database that is maintained by the Research Department at the Federal Reserve Bank of St.Louis. 
 The variables collected from the FRED website are Gross Domestic Product (Billions of Dollars, Quarterly, Seasonally Adjusted Annual Rate), Population (Thousands, Quarterly, Not Seasonally Adjusted), Market Yield on U.S.
@@
 \section*{Methods}
-To investigate which factors influence Gross Domestic Product, Ordinary Least Squares Regressiion will be used. 
+To investigate which factors influence Gross Domestic Product, Ordinary Least Squares Regression will be used. 
 Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
@@
 This is because the P-Value of the F-Test is less than $2.2 * 10^{-16}$.
-The variables TCMR, DPI, UNRATE and BSLP are significant in this model, whereas the variables TPEC and POP are not significantly differnt from zero at the 5\% level of significance.  
-The Multiple R-Squared value indicates that this model is a good fit since 99.73\% of the variablity in the data is explated by the model. 
+The variables TCMR, DPI, UNRATE and BSLP are significant in this model, whereas the variables TPEC and POP are not significantly different from zero at the 5\% level of significance.  
+The Multiple R-Squared value indicates that this model is a good fit since 99.73\% of the variablity in the data is explained by the model. 
 Model 1 found significant relationships between the frequency of GDP and the variables TCMR, DPI, UNRATE and BSLP. 
@@
 Next, and AIC test will be applied to Model 1 and Model 2 application to validation data. 
-This tested resulted in Model 1 reciving and AIC of 559.5405, and Model 2 557.1234. 
-Since Model 2 recived a lower AIC it has the most adequate fit with the least variables when built using validation data. 
+This tested resulted in Model 1 receiving and AIC of 559.5405, and Model 2 receiving an AIC of 557.1234. 
+Since Model 2 received a lower AIC, it has the most adequate fit with the least variables when built using validation data. 
 The regression equation results are as follows: 
 \begin{equation}
-  GDP = -919.82242+50.18851(TCMR)+1.20921(DPI)-81.67410(UNRATE)+28.06281(BSPL)
+  GDP = -919.822+50.188(TCMR)+1.209(DPI)-81.674(UNRATE)+28.062(BSPL)
 \end{equation}
@@
 There is no unique set of factors discovered yet that predict GDP. 
-This paper showed that TCMR, DPI, UNRATE, and BSPL have a significant relationship with GDP.
+This paper showed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rate have a significant relationship with GDP.
 These variables were selected with author subjectivity, and this is important to take into consideration. 
-This paper did not show any significant relationship between Total Primary Energy Consumption and GDP in the United States. 
-It is also important to consider that the homoscedacity assumption of OLS Regression is questionable in this paper. 
+This paper did not show any significant relationship between Total Primary Energy Consumption or Population with GDP in the United States. 
+It is also important to consider that the homoscedacity assumption of Ordinary Least Squares Regression is questionable in this paper. 
 For future studies, to limit this violation the data could be transformed.
 This research is a introductory study into the relationship between energy consumption and economic growth. 
+Even though this study showed that there is no significant relationship between GDP and Enery Consumption, this relationship should be investigated further.
+Energy is such a vital part of society in the United States, and if a relationship between GDP and Energy Consumption is found, this can be vital for economists in many counties.
 This could be a useful start point for economic developers to identify signals of crucial moments to allow policy makers to make more informed decisions.

### 2022-12-09 Manuscript/manuscript.tex
commit

@@
 Even though this study showed that there is no significant relationship between GDP and Enery Consumption, this relationship should be investigated further.
-Energy is such a vital part of society in the United States, and if a relationship between GDP and Energy Consumption is found, this can be vital for economists in many counties.
+Energy is such a vital part of society in the United States, and if a significant relationship between GDP and Energy Consumption is found, this can be vital for economists in many counties.
 This could be a useful start point for economic developers to identify signals of crucial moments to allow policy makers to make more informed decisions.
